Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-09 src/tex/ms.tex
Add placeholder to Appendix
Update violin plot
Edit figures

\begin{figure}
    \script{birefringence.py}
    \includegraphics[width=\columnwidth]{figures/birefringence.pdf}
    \caption{
        The observed Fourier amplitude of two polarizations of a simulated GW signal with and without birefringence.
        The amplitudes, as GR predicts, are shown in dotted lines with blue and orange colors representing the left-handed and right-handed polarizations.
        The amplitudes with birefringence are shown in solid lines with blue and orange colors representing the left-handed and right-handed polarizations.
        This plot shows the effect of amplitude birefringence with frequency dependence.
        \mi{@Thomas can you add a panel with the time-domain waveforms (maybe just for L or R)?}
    }
    \label{fig:birefringence}
\end{figure}

@@

We carry out \ac{PE} using a custom version of \textsc{Bilby} \citep{Bilby}, that applies Eq.~\eqref{eq:waveform_modification} for any \ac{GR} baseline waveform.
We depart from the \ac{PE} configuration as in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, with \textsc{IMRPhenomXPHM} as the reference waveform.
We apply a distance prior uniform in comoving volume instead of a power law distribution used in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, and set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$.

@@

\begin{figure*}
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 70 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The blue horizontal solid line represents the median of the restricted posterior of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval of the restricted posterior of $\kappa$.
        The pink horizontal solid line represents $\kappa=0$.
    }
    \label{fig:violin_kappa}
\end{figure*}
% show the excluded events visually different

@@

\appendix
\section{}

>>>>

\begin{figure}
    \script{birefringence_frequency_domain.py}
    \includegraphics[width=\columnwidth]{figures/birefringence_frequency_domain.pdf}
    \caption{
        The observed Fourier amplitude of two polarizations of a simulated GW signal with and without birefringence.
        The amplitudes, as GR predicts, are shown in dotted lines with blue and orange colors representing the left-handed and right-handed polarizations.
        The amplitudes with birefringence are shown in solid lines with blue and orange colors representing the left-handed and right-handed polarizations.
        This plot shows the effect of amplitude birefringence with frequency dependence.
        \mi{@Thomas can you add a panel with the time-domain waveforms (maybe just for L or R)?}
    }
    \label{fig:birefringence_frequency_domain}
\end{figure}

@@

We carry out \ac{PE} using a custom version of \textsc{Bilby} \citep{Bilby}, that applies Eq.~\eqref{eq:waveform_modification} for any \ac{GR} baseline waveform.
We depart from the \ac{PE} configuration as in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, with \textsc{IMRPhenomXPHM} as the reference waveform.
We apply a distance prior which is uniform in comoving volume and source frame time instead of a power law distribution used in \citet{GWTC-2.1, GWTC-3, GWTC-2.1_dataset, GWTC-3_dataset}, and set the prior on $\kappa$ to a uniform distribution between $-1$ and $1$.

@@

\begin{figure*}
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for 70 events in this study.
        Each violin represents a different event.
        The color of the violins represents the quotient of the median and standard deviation of the posterior.
        The blue horizontal solid line represents the median of the restricted posterior of $\kappa$, and the blue dashed lines enclose the $90\%$ confidence interval of the restricted posterior of $\kappa$.
        The pink horizontal solid line represents $\kappa=0$.
        GW200129 is shown with light blue edges, as it is excluded from the calculation of collective analysis.
    }
    \label{fig:violin_kappa}
\end{figure*}

@@

\appendix
\label{sec:corner_plots}
\begin{figure}[h]
    \script{corner_GW170818.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW170818.pdf}
    \caption{Corner plot of GW170818.}
    \label{fig:corner_GW170818}
\end{figure}

\begin{figure}[h]
    \script{corner_GW200129.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW200129.pdf}
    \caption{Corner plot of GW200129.}
    \label{fig:corner_GW200129}
\end{figure}

\begin{figure}[h]
    \script{corner_GW200224.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW200224.pdf}
    \caption{Corner plot of GW200224.}
    \label{fig:corner_GW200224}
\end{figure}

% \begin{figure}
%     \script{birefringence_time_domain.py}
%     \includegraphics[width=\columnwidth]{figures/birefringence_time_domain.pdf}
%     \caption{
%         % The observed Fourier amplitude of two polarizations of a simulated GW signal with and without birefringence.
%         % The signal, as GR predicts, is shown in the upper panel, and the signal with birefringence is shown in the lower panel.
%         % The signals in the upper panel are shown in dashed blue and dotted orange lines representing the left-handed and right-handed polarizations.
%         % Note that the 
%         % The amplitudes with birefringence are shown in solid lines with blue and orange colors representing the left-handed and right-handed polarizations.
%         This plot shows the effect of amplitude birefringence with frequency dependence.
%     }
%     \label{fig:birefringence_time_domain}
% \end{figure}
